Estimating nucleon substructure properties in a\\[.2ex] unified hydrodynamic model of p-Pb and Pb-Pb collisions

### 2018-05-05 talk/qm2018.tex
move log transform to init
Add some slides

\begin{frame}[b, plain]{\scshape Parameter estimates from lead-lead collisions}
  \begin{columns}[b]
    \begin{column}{.43\textwidth}
      \includegraphics<1>[width=\textwidth]{lead_observables_design}
      \includegraphics<2>[width=\textwidth]{lead_observables_posterior}
    \end{column}
    \begin{column}{.57\textwidth}
      \begin{itemize}
        \item Combined analysis of 2.76 and 5.02
          TeV beam energies \textcolor{theme}{\scshape (New!)} 
        \item Parametric initial conditions and medium parameters\
        \item Quantitative estimates on $\eta/s$ and $\zeta/s$ with meaningful uncertainties
        \item See thesis by Jonah Bernhard {\small [\textcolor{theme}{\url{1804.06469}}]}
      \end{itemize}
      \bigskip
      \includegraphics<1>[width=\textwidth]{region_shear_bulk}
      \includegraphics<2>[width=\textwidth]{region_shear_bulk}
    \end{column}
  \end{columns}
  \medskip
\end{frame}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{pb208}\\
        Pb$^{208}$ nucleus
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon radii from spherical or deformed Woods-Saxon distributions
        \item Euler angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleon for lumpy nucleon
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{gaussian_proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{deformed_proton}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (6.0, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.2cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<2>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1-2>[->, thick, theme] (b2.west) to [out=180, in=90] (-.58, 1.3);
    \draw<1-2>[->, thick, theme] (b3.west) to [out=180, in=90] (-.05, 0);
    \node<3>[xshift=-2.8cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[xshift=-1.2cm, yshift=1.6cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[xshift=-.7cm, yshift=1.1cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Maximum a posteriori parameters}
  \includegraphics[height=.8\textheight]{find_map}
\end{frame}

\begin{frame}{\scshape Posterior nucleon shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
    \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Parton sampling radius (approx nucleon width) is not well constrained\\[2ex]
        \item Analysis prefers small partons,\\
          $w_\text{parton} = 0.38_{-0.18}^{+0.21}$~fm\\[2ex]
        \item[\small\faicon{exclamation-triangle}] Results are likely sensitive to assumed
          details of the model, e.g.\ equation of state, pre-equilibirum dynamics and viscous
          corrections to freezeout
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}[b, plain]{\scshape Parameter estimates from lead-lead collisions}
  \begin{columns}[b]
    \begin{column}{.43\textwidth}
      \includegraphics<1>[width=\textwidth]{lead_observables_design}
      \includegraphics<2>[width=\textwidth]{lead_observables_posterior}
    \end{column}
    \begin{column}{.57\textwidth}
      \begin{itemize}
        \item Combined analysis of 2.76 and 5.02
          TeV beam energies \textcolor{theme}{\scshape (New!)} 
        \item Parametric initial conditions and medium parameters\
        \item Quantitative estimates on $\eta/s$ and $\zeta/s$ with meaningful uncertainties
        \item See thesis by Jonah Bernhard {\small [\textcolor{theme}{\url{1804.06469}}]}
      \end{itemize}
      \bigskip
      \includegraphics<1>[width=\textwidth]{fig/region_shear_bulk_blank}
      \includegraphics<2>[width=\textwidth]{fig/region_shear_bulk}
    \end{column}
  \end{columns}
  \medskip
\end{frame}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{pb208}\\
        Pb$^{208}$ nucleus
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon radii from spherical or deformed Woods-Saxon distributions
        \item Euler angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleons for lumpy nucleons
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{gaussian_proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{deformed_proton}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (6.0, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (-.35, .8);
    \draw<1>[->, thick, theme] (b3.west) to [out=180, in=90] (.1, -.95);
    \node<2>[xshift=-2.7cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_p}\\[2ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    \node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<3>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_parton_number}\\[2ex]
        \small Evidence for nucleon substructure $N_\text{partons} > 1$.\\
        \small Does not prefer a specific parton number.
      };
    \node<4>[xshift=.62cm, yshift=-.15cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_freestreaming}\\[2ex]
        \small Analysis cannot tolerate free-streaming\\
        \small times larger than ${\sim} 1$~fm/$c$
      };
    \node<5>[xshift=-.5cm, yshift=.9cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_structure}\\[2ex]
        \small Parton structure parameter $\chi_\mathrm{struct} = 0.28_{-0.16}^{+0.17}$,\\
        \small Was used to reparametrize parton width as\\[.5ex]
        \small $v = v_\text{min} + \chi_\text{struct}(w - v_\text{min})$.\\[1ex]
        \small \hfill Let's revert $\chi_\text{struct}$ back to a width...
      };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Nucleon width\, $w = 0.9_{-0.14}^{+0.16}$~fm\\[.5ex]
          (consistent with rms charge radius)\\[2ex]
        \item Parton width\, $v = 0.4_{-0.14}^{+0.16}$~fm\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibirum dynamics and viscous
          corrections $\delta f$\\[2ex]
        \item Nevertheless tantalizing question, can hydro be used
          to measure the size and shape of the proton?
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP viscosities}
  \bigskip
  \begin{columns}
    \begin{column}{.6\textwidth}
      \includegraphics[width=\textwidth]{fig/region_shear_bulk_blank}\\[2ex]
      \includegraphics[width=\textwidth]{fig/region_shear_bulk}
    \end{column}
    \begin{column}{.4\textwidth}
      p-Pb \& Pb-Pb at 5.02 TeV
    \end{column}
  \end{columns}
\end{frame}
